Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2018-11-30 awipev-CO2.Rmd
hashtag

# to create periods according to TA deployments
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00", 
              "2018-01-07 00:00:00", "2018-06-20 00:00:00",  "2018-07-31 00:00:00","2018-10-30 18:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))

>>>>

##
# to create periods according to TA deployments
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00", 
              "2018-01-07 00:00:00", "2018-06-20 00:00:00",  "2018-07-31 00:00:00","2018-10-30 18:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
